\section{Google Scholar Search Results}
The Google Scholar search for "organizational inertia" on 8 July 2020 returned the following results:\\
\begin{itemize}
\item \cite{kelly1991organizational} cited 1,202 times. PDF is available.
\item \cite{dean1991integrated} cited 573 times. No PDF is available.
\item \cite{barnett2008red} cited 125 times. PDF is available.
\item \cite{geiger2009narratives} cited 120 times. PDF is available.
\item \cite{shimizu2005constrains} cited 218 times. PDF is available.
\item \cite{van1998bridging} cited 207 times. PDF is available.
\item \cite{snell1994strategic} cited 219 times. No PDF is available.
\item \cite{lazerson1999resisting} cited 140 times. No PDF is available.
\item \cite{dobrev2003shifting} cited 175 times. PDF is available.
\item \cite{godkin2008overcoming} cited 72 times. PDF is available.
\item \cite{larsen2002representing} cited 115 times. PDF is available.
\item \cite{boyer2006organizational} cited 57 times. PDF is available.
\item \cite{naslund2012appropriated} cited 109 times. No PDF is available.
\item \cite{dean1993determinants} cited 76 times. No PDF is available.
\item \cite{nedzinskas2013impact} cited 49 times. PDF is available.
\item \cite{hannan2002structural} cited 27 times. PDF is available.
\item \cite{lorenz1994organizational} cited 31 times. No PDF is available.
\item \cite{chiu2004hollowing} cited 32 times. No PDF is available.
\item \cite{allcorn2011workplace} cited 18 times. No PDF is available.
\item \cite{godkin2010zone} cited 32 times. No PDF is available.
\item \cite{bromley1992vested} cited 18 times. PDF is available.
\item \cite{majid2011organizational} cited 13 times. PDF is available.
\item \cite{buchta2003technological} cited 15 times. No PDF is available.
\item \cite{besson2012strategizing} cited 320 times. PDF is available.
\item \cite{hannan1986uncertainty} cited 87 times. No PDF is available.
\item \cite{haag2014organizational} cited 11 times. No PDF is available.
\item \cite{nedzinskas2014dynamic} cited 12 times. PDF is available.
\item \cite{reger1994creating} cited 248 times. PDF is available.
\item \cite{chen2014revisiting} cited 19 times. PDF is available.
\item \cite{hung2015sustained} cited 12 times. PDF is available.
\end{itemize}

Of the 30 results selected, 18 have freely available PDF files available for downloaded.\\

It is worrying that only 13 have been cited more than 100 times. And only one have been cited more than 1,000 times.\\
